### 2023-01-13 source/paper/main.tex
#16 Test parallel trends for high/low
#16 Fix UCR data, rerun analysis
#16 Check pretrends for 2010 high/low marijuana arrests
#16 Update year range of pre0trends

\begin{center}
\includegraphics[width=.4\textwidth]{college_enroll_byrace_1986.png}
\includegraphics[width=.4\textwidth]{college_enroll_bysex_1986.png}
\includegraphics[width=.4\textwidth]{college_enroll_byrace_2010.png}
\includegraphics[width=.4\textwidth]{college_enroll_bysex_2010.png}
\end{center}

\begin{center}
  \includegraphics[width=.4\textwidth]{faminc_byrace_1986.png}
  \includegraphics[width=.4\textwidth]{faminc_bysex_1986.png}
  \includegraphics[width=.4\textwidth]{faminc_byrace_2010.png}
  \includegraphics[width=.4\textwidth]{faminc_bysex_2010.png}
  \end{center}

@@

>>>>

Note: all figures are limited to ages 18-24 inclusive.

\begin{center}
\includegraphics[width=.4\textwidth]{pretrends/1986/college_enroll_byrace_1986.png}
\includegraphics[width=.4\textwidth]{pretrends/1986/college_enroll_bysex_1986.png}
\includegraphics[width=.4\textwidth]{pretrends/2010/college_enroll_byrace_2010.png}
\includegraphics[width=.4\textwidth]{pretrends/2010/college_enroll_bysex_2010.png}
\end{center}

\begin{center}
  \includegraphics[width=.4\textwidth]{pretrends/1986/faminc_byrace_1986.png}
  \includegraphics[width=.4\textwidth]{pretrends/1986/faminc_bysex_1986.png}
  \includegraphics[width=.4\textwidth]{pretrends/2010/faminc_byrace_2010.png}
  \includegraphics[width=.4\textwidth]{pretrends/2010/faminc_bysex_2010.png}
\end{center}

\includegraphics[width=0.7\textwidth]{pretrends/1986/college_enroll_bydrugarrests_1986.png}

\includegraphics[width=0.7\textwidth]{pretrends/2010/college_enroll_bydrugarrests_2010.png}

\includegraphics[width=0.7\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_1986.png}

\includegraphics[width=0.7\textwidth]{eventstudy/high_drug_use/high_marijuana_eventstudy_2010.png}

@@

\import{../../output/tables/}{ddd_1986.tex}
